---
name: Antonio
surname: Páez
position: "Professor"
address: |
         | School of Earth, Environment and Society
         | McMaster University
         | 1280 Main St West, Hamilton, Ontario, Canada L8S 1S4
phone: +1 905 525 9140
www: experts.mcmaster.ca/display/paezha
email: "paezha@mcmaster.ca"
orcid: 0000-0001-6912-9919
github: paezha
publons: 2897251
#researchgate: 7004827878
googlescholar: paezha
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    page_total: true
    extra_dependencies: ["flafter"]
---

```{r knitr-setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE,
                      fig.show = "asis", 
                      # Width of figures in output document is 60% of linewidth
                      out.width = "0.6\\linewidth", 
                      fig.align = "center")
```

```{r current-year}
# Retrieve current year
current_year <- as.numeric(as.character(Sys.time(), '%Y')) # Update year
```

```{r load-packages}
library(dplyr) # Data carpentry
library(ggplot2) # Grammar of graphics
library(here) # Package to simplify finding files within projects
library(readr) # Package to read external data, e.g., csv files
library(scholar) # Package to analyze citation data from Google Scholar
library(tibble) # Package to work with simple data frames
library(vitae) # Templates and functions to simplify the production and maintenance of curriculum vitae.
```

# About me

* I trained in civil engineering before being adopted into geography.
* My areas of interest include spatial analysis, spatial statistics, transportation, travel behavior, cities.
* Also, too, mathematics, computer languages, science fiction, poetry, and memes.
* I have been known to look professorial on occasion.
* At this rate my only hope of being recognized is as the most promising oldest researcher in my discipline.

<!--
# My places

```{r my-places-plot,fig.align='center', out.width="1.0\\linewidth"}
# THIS CODE IS ADAPTED FROM LORENA ABAD'S AWESOME CV: https://github.com/loreabad6/R-CV
library(emojifont)
library(sf)
library(sfnetworks)
library(rnaturalearth) # Package to work with Natural Earth map data

load.fontawesome()
edu <- fontawesome("fa-book")
work <- fontawesome("fa-briefcase")

places <- read_csv(paste0(here(),
                          "/assets/places.csv")) %>%
  st_as_sf(coords = c("long",
                      "lat"), 
           crs = 4326) %>%
  mutate(Year = as.Date(as.character(Year), format = "%Y", origin = "1970-01-01"),
         label = case_when(Activity == "Education" ~ paste(edu),
                           Activity == "Work" ~ paste(work)))

as.Date_origin <- function(x){
  as.Date(x, origin = '1970-01-01')
}

# Retrieve boundaries of countries
world <- ne_countries("medium", 
                      returnclass = 'sf')

# Create ggplot object
ggplot() +
  # Plot boundaries of countries
  geom_sf(data = world, 
          color = 'black', 
          lwd = 0.2) +
  # Add text with icons
  geom_sf_text(data = places,
               aes(label = label,
                   color = Year),
               family = "fontawesome-webfont",
               size = 3) +
  # Project coordinates
  coord_sf(crs = '+proj=robin') +
  # Specify color scale parameters (palette and direction)
  scale_color_distiller(palette = "OrRd",
                        direction = 1,
                        labels = as.Date_origin,
                        breaks = as.Date_origin(c("1980-01-01", 
                                                  "1990-01-01", 
                                                  "2000-01-01"))) +
  theme(legend.text=element_text(family='fontawesome-webfont')) +
  # Set theme
  theme_void() +
  # Set margins
  theme(plot.margin = margin(-1, 0, -0.5, 0, "cm"))
```
-->

# Education

```{r education-details}
# Read assets and pass to detailed_entries()
read_csv(paste0(here(),"/assets/education.csv")) %>% 
  detailed_entries(what = Degree, 
                   when = Year, 
                   with = Institution,
                   where = Where, 
                   why = Thesis,
                   # Inputs will be parsed as LaTeX code when .protect=FALSE
                   .protect = FALSE)
```

# Current Status at McMaster

Full Professor in the School of Earth, Environment and Society since 2014. Tenured since 2007.

# Employment History

## Academic

```{r employment-details}
# Read assets and pass to detailed_entries()
read_csv(paste0(here(),"/assets/employment.csv")) %>% 
  detailed_entries(what = Position, 
                   when = Year, 
                   with = Organization,
                   where = Where,
                   .protect = FALSE)
```

## Industry

Surveyor and construction site supervisor (August 1993 – March 1995) Topographical
survey projects in Nuevo León, Mexico, sponsored by various Municipal Public Works Departments (Monterrey, Guadalupe, Santa Catarina), and by Mercedes-Benz. These projects involved in-field data collection and computer aided design. Construction site supervision.

\newpage

# Areas of Interest

Spatial data analysis and statistics; transportation modeling; travel behavior; health geography; Geographic Information Systems.

# Honours

## Visiting Professorships

```{r professorship-details}
read_csv(paste0(here(),"/assets/honors.csv")) %>%
  # Filter honors of type "Professorship"
  dplyr::filter(Type == "Professorship") %>% 
  detailed_entries(what = Honor, 
                   when = Year, 
                   with = Organization,
                   where = Where,
                   .protect = FALSE)
```

## Scholarships

```{r scholarships-details}
read_csv(paste0(here(),"/assets/honors.csv")) %>%
  # Filter honors of type "Scholarship"
  dplyr::filter(Type == "Scholarship") %>% 
  detailed_entries(what = Honor, 
                   when = Year, 
                   with = Organization,
                   where = Where,
                   .protect = FALSE)
```

## Scientific Awards

```{r scientific-awards-details}
read_csv(paste0(here(),"/assets/honors.csv")) %>%
  # Filter honors of type "Scientific Awards"
  dplyr::filter(Type == "Scientific Awards") %>% 
  detailed_entries(what = Honor, 
                   when = Year, 
                   with = Organization,
                   where = Where,
                   why = With,
                   .protect = FALSE)
```

# Research Impact

Fig. \ref{fig:citations} is a summary of research impact according to Google Scholar.

```{r citations-plot, fig.cap="\\label{fig:citations}Citations per year according to Google Scholar"}
id <- "bLY377kAAAAJ" # Replace with your own google scholar id
# For example: https://scholar.google.ca/citations?user=yZP0dXsAAAAJ&hl=en&oi=ao
citations_scholar <- scholar::get_citation_history(id)

citations_scholar %>%
  ggplot() + 
  geom_col(aes(x = year, 
               y = cites),
           color = "black",
           fill = "white") + 
  annotate(geom = "text", 
           x = 2004, 
           y = 950, 
           hjust = 0,
           label = paste0("Total cites = ", 
                          prettyNum(get_profile(id)$total_cites, big.mark = ","))) +
  annotate(geom = "text", 
           x = 2004, 
           y = 900, 
           hjust = 0,
           label = paste0("h-index = ", 
                          as.character(get_profile(id)$h_index))) +
  annotate(geom = "text", 
           x = 2004, 
           y = 850, 
           hjust = 0,
           label = paste0("i10-index = ", 
                          as.character(get_profile(id)$i10_index))) +
  ggthemes::theme_tufte()
```

# Lifetime Publications

## Journal Articles

```{r refereed-publications}
bibliography_entries(paste0(here(),"/assets/refereed-publications.bib")) %>%
  #bibliography_entries(paste0(here(),"/assets/savedrecs_2.bib")) %>%
  arrange(desc(issued), desc(author$family))
```
